---
title: "gabovicen_peercommentary_inovick_02"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions


Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.


1) What is the probability that she will hear more than 8 calls during any given session?

```{r}
1-dpois(8,15)
```


2) What is the probability that she will hear no calls in a session?

```{r}
dpois(0,15)
```


3) What is the probability that she will hear exactly 3 calls in a session?

```{r}
dpois(3,15)
```


4) Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l = 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")
```



5) Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
rpois(104, 15)
```


6) Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
library(ggplot2)
x <- rpois(104, 15)  # simulate from a normal distribution with mean 5 and SD 8
hist(x,xlim=c(0,30),xlab = "Number of Calls", main = "Histogram of Calls")
```
## we did some of these differently but yours is concise, looks good, and works. Nice!